---
title: "Comparing the proportion of CIs"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading Data
```{r warning=F, message=F}
library(tximport)
source("helper_func.R")
load("out_1/sim_counts_matrix.rda")
dir <- "out"

gsFiles <- file.path(dir, c("ERR188297_GS", "sample_01_GS", "sample_01_GS_150", "sample_01_GS_200"), "quant.sf")
txiInfRepGS <- tximport(gsFiles, type = "salmon", txOut = TRUE)

bootFiles <- file.path(dir, c("ERR188297_B", "sample_01_B"), "quant.sf")
txiInfRepBoot <- tximport(bootFiles, type = "salmon", txOut = TRUE)

txiInfRepGS <- computeConfInt(txiInfRepGS)
txiInfRepBoot <- computeConfInt(txiInfRepBoot)

depthSim <- sum(counts_matrix[,1])
depthSal <- sum(txiInfRepBoot$counts[,2])

reqSim <- counts_matrix[,1]*(depthSal/depthSim)

print(abs(sum(reqSim) - sum(txiInfRepBoot$counts[,2])) < 1e-5)

sum(rownames(txiInfRepBoot$conf[[2]]) != rownames(txiInfRepGS$conf[[2]])) == 0 ## Checking transcripts names match across BS and GS
sum(rownames(txiInfRepGS$conf[[2]]) != rownames(txiInfRepGS$counts[,2])) == 0 ## Checking transcripts names match across the counts

mInds <- match(rownames(counts_matrix), rownames(txiInfRepBoot$conf[[2]])) ##Indexes of transcripts of simulated data within txi
```

### Plotting Simulated (True) vs Generated
```{r}
plot(log2(reqSim), log2(txiInfRepGS$counts[mInds, 2])) + abline(coef = c(0,1))
```

### Computing the Coverage for the 1st sample of simulated data
```{r warning=F, message=F}
confBootReq <- txiInfRepBoot$conf[[2]][mInds,]
confGSReq <- vector(mode = "list", 3)
names(confGSReq) <- c("GS100", "GS150", "GS200")
for(i in c(2:4))
    confGSReq[[i-1]] <- txiInfRepGS$conf[[i]][mInds,]

confMat <- list(confGSReq[[1]], confGSReq[[2]], confGSReq[[3]], confBootReq)
names(confMat) <- c("GS100", "GS150", "GS200", "BS100")

covOverall <- sapply(confMat, function(mat) computeCoverage(reqSim, mat, list(seq(nrow(counts_matrix)))))

cInds100 <- extractBinInds(reqSim, breaks = 100)
cov100 <- createCovDf(confList = confMat, counts = reqSim, cInds100)

cIndsAll <- extractBinInds(reqSim, breaks = NULL)
covAll <- createCovDf(confList = confMat, counts = reqSim, cIndsAll)
```

### Overall Coverage
```{r}
print(covOverall)
```

### Plotting for 100 bins
First, unique counts across transcripts are computed and then partitioned into 100 bins. Accordingly trasncripts arranged into bins.
Plot 1 repesents the number of transcripts (log) in each bin (log scale)
Plot 2 shows the corresponding coverage across the bins
```{r}
plot(x=log2(as.numeric(names(cInds100))), y = log2(sapply(cInds100, function(x) length(x))))
plotCovDf(cov100, line = T)
```

###  Plotting for all
Similar to above, however each bin represents a unique count
```{r}
plot(x = log2(as.numeric(names(cIndsAll))), y = log2(sapply(cIndsAll, function(x) length(x))))
plotCovDf(covAll)
```

### InfReps
```{r}
infRVs <- computeInfRep(confMat[c(1,4)])
quantGS <- quantile(infRVs[[1]], probs = c(0.10, 0.90))
quantBoot <- quantile(infRVs[[2]], probs = c(0.10, 0.90))

indsLowRV <- list("GS" = which(infRVs[[1]] <= quantGS[1]), "Boot" = which(infRVs[[2]] <= quantBoot[1]))
indsHighRV <- list("GS" = which(infRVs[[1]] >= quantGS[2]), "Boot" = which(infRVs[[2]] >= quantBoot[2]))

quantExp <- quantile(txiInfRepGS$counts[mInds,2], probs = c(0.10, 0.90))
indsExp <- list("High" = which(txiInfRepGS$counts[mInds,2] >= quantExp[2]), "Low" = which(txiInfRepGS$counts[mInds,2] <= quantExp[1]))
```

### Plotting Coverage for Expression and InfReps (100 Inf Replicates)
```{r}
library(ggpubr)
dfCov <- sapply(confMat[c(1,4)], function(mat) computeCoverage(reqSim, mat, list(seq(nrow(counts_matrix))), F))

pHigh <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]),list("GS"=indsExp[["High"]], "Boot" = indsExp[["High"]]))
pLow <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]),list("GS"=indsExp[["Low"]], "Boot" = indsExp[["Low"]]))
pExp <- ggarrange(pHigh, pLow, labels = c("High Expression", "Low Expression"))
annotate_figure(pExp, top = text_grob(paste("Total transcripts with coverage 1 by expression out of", length(indsExp[["High"]]), "Transcripts")))

pHighInf <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]),list("GS"=indsHighRV[["GS"]], "Boot" = indsHighRV[["Boot"]]))
pLowInf <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]),list("GS"=indsLowRV[["GS"]], "Boot" = indsLowRV[["Boot"]]))
pInf <- ggarrange(pHighInf, pLowInf, labels = c("High Inferential Variance", "Low Inferential Variance"))
annotate_figure(pInf, top = text_grob(paste("Total transcripts with coverage 1 by Inf Variance out of", length(indsLowRV[["Boot"]]), "Transcripts")))

```

### High Inf by expression
```{r}
highInfGS <- list("HighExp" = intersect(indsHighRV[["GS"]], indsExp[["High"]]), 
                  "LowExp" = intersect(indsHighRV[["GS"]], indsExp[["Low"]]))
highInfBoot <- list("HighExp" = intersect(indsHighRV[["Boot"]], indsExp[["High"]]), 
                  "LowExp" = intersect(indsHighRV[["Boot"]], indsExp[["Low"]]))

pHighInfH <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]), list("GS" = highInfGS[["HighExp"]], "Boot" = highInfBoot[["HighExp"]]), title = T)
pHighInfL <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]), list("GS" = highInfGS[["LowExp"]], "Boot" = highInfBoot[["LowExp"]]), title = T)
pHighInf <- ggarrange(pHighInfH, pHighInfL, labels = c("High Exp", "Low Exp"))
annotate_figure(pHighInf, top = text_grob(paste("High Inferential Variance Transcripts")))
```

### Low Inf by expression
```{r}
lowInfGS <- list("HighExp" = intersect(indsLowRV[["GS"]], indsExp[["High"]]), 
                  "LowExp" = intersect(indsLowRV[["GS"]], indsExp[["Low"]]))
lowInfBoot <- list("HighExp" = intersect(indsLowRV[["Boot"]], indsExp[["High"]]), 
                  "LowExp" = intersect(indsLowRV[["Boot"]], indsExp[["Low"]]))

pLowInfL <- plotBarplot(list("GS"=dfCov[,1],"Boot"=dfCov[,2]), list("GS" = lowInfGS[["LowExp"]], "Boot" = lowInfBoot[["LowExp"]]), title = T)
print(pLowInfL)
```