---
title: "Comparing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading data and computing coverages
```{r warning=F,message=F}
source("helper_func.R")
suppressPackageStartupMessages(library(SummarizedExperiment))
load("environment/seList.RData")
load("../../real_data/out_1/sim_counts_matrix.rda")

se100 <- seList[["100"]]
se100 <- computeSizeFactors(se100, counts_matrix[,1])
se100 <- computeConfInt(se100, sf = T)
covInds <- computeCoverage(counts_matrix[,1], se100, list(seq(nrow(counts_matrix))), prop = F)[[1]]
```

### Number of transcripts that are covered by all the 3 methods
```{r}
commInds <- Reduce(intersect, covInds)
print(length(commInds))
```

### Transcripts that are covered by only 1 method
```{r}
library(VennDiagram)
bootOnly <- setdiff(setdiff(covInds[[1]],covInds[[2]]), covInds[[3]])
gibbsOnly <- setdiff(setdiff(covInds[[2]],covInds[[1]]), covInds[[3]])
poleeOnly <- setdiff(setdiff(covInds[[3]],covInds[[1]]), covInds[[2]])

g <- venn.diagram(covInds, category.names=names(covInds), filename=NULL, output=T)
grid.draw(g)
```

### Number of transcripts for which the width is lower across the common covered transcripts
```{r}
minInds <- apply(assays(se100)[["Width"]][commInds, ], 1, which.min)
tb <- table(minInds)
names(tb) <- c("Boot", "Gibbs", "Polee")
print(tb)
```

### Number of transcripts for which the width is lower across the common covered transcripts only b/w boots and GS removing other common transcripts
```{r}
bGSInds <- setdiff(intersect(covInds[[1]], covInds[[2]]), commInds)
minInds <- apply(assays(se100)[["Width"]][bGSInds, 1:2], 1, which.min)
tb <- table(minInds)
names(tb) <- c("Boot", "Gibbs")
print(tb)
```

### Number of transcripts for which the width is lower across the common covered transcripts only b/w boots and Polee removing other common transcripts
```{r}
bPolInds <- setdiff(intersect(covInds[[1]], covInds[[3]]), commInds)
minInds <- apply(assays(se100)[["Width"]][bPolInds, c(1,3)], 1, which.min)
tb <- table(minInds)
names(tb) <- c("Boot", "Polee")
print(tb)
```

### Number of transcripts for which the width is lower across the common covered transcripts only b/w Gibbs and Polee removing other common transcripts
```{r}
gPolInds <- setdiff(intersect(covInds[[2]], covInds[[3]]), commInds)
minInds <- apply(assays(se100)[["Width"]][gPolInds, c(2,3)], 1, which.min)
tb <- table(minInds)
names(tb) <- c("Gibbs", "Polee")
print(tb)
```