---
title: "EDA"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading data
100 gibbs samples and bootstrap
```{r warning=FALSE, message=FALSE}
library(tximport)
source("helper_func.R")
load("out_1/sim_counts_matrix.rda")
dir <- "out"
gsFiles <- file.path(dir, c("ERR188297_GS", "sample_01_GS"), "quant.sf")
txiInfRepGS <- tximport(gsFiles, type = "salmon", txOut = TRUE)

bootFiles <- file.path(dir, c("ERR188297_B", "sample_01_B"), "quant.sf")
txiInfRepBoot <- tximport(bootFiles, type = "salmon", txOut = TRUE)

#fileDf <- vroom::vroom("fastq/sample_01_1.fastq.gz", delim = "\n", col_names = F)
#simCounts <- countReads(fileDf)

txiInfRepGS <- computeConfInt(txiInfRepGS)
txiInfRepBoot <- computeConfInt(txiInfRepBoot)
```

### Simulated Data

#### Obtaining the transcripts with zero counts
```{r}
zeroBInds <- which(txiInfRepBoot$counts[,2] == 0)
zeroGSInds <- which(txiInfRepGS$counts[,2] == 0)
print(length(zeroGSInds))
print(length(zeroBInds))
print(length(setdiff(zeroGSInds, zeroBInds)))
print(length(setdiff(zeroBInds, zeroGSInds)))
```

So mostly same transcripts have zero counts at two independent EM runs

#### Obtaining transcripts that have zero means over the bootstrap runs
```{r}
zeroMeanGS <- which(txiInfRepGS$conf[[2]][,3] <= 3)
zeroMeanB <- which(txiInfRepBoot$conf[[2]][,3] <= 3)

print(length(zeroMeanGS))
print(length(zeroMeanB))
print(length(setdiff(zeroBInds, zeroMeanB)))
print(length(setdiff(zeroGSInds, zeroMeanGS)))
print(length(intersect(zeroMeanB, zeroMeanGS)))

plotDfZeros <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[2]], "GS" = txiInfRepGS$conf[[2]]), list("Boot" = setdiff(zeroBInds, zeroMeanB), "GS" = setdiff(zeroGSInds, zeroMeanGS)))
plotHist(plotDfZeros, "Width")
plotHist(plotDfZeros, "Mean")
plotHist(plotDfZeros, "Var")
```

A lot of transcripts that had zero counts under Gibbs sampling have non zero means compared to bootstrap

#### Only observing the transcripts having non zero counts
```{r}
nZeroInds <- setdiff(1:nrow(txiInfRepBoot$conf[[2]]), union(zeroBInds, zeroGSInds))
print(length(nZeroInds))
plotDfNonZeros <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[2]], "GS" = txiInfRepGS$conf[[2]]), 
                               list("Boot" = nZeroInds, "GS" = nZeroInds))
plotViol(plotDfNonZeros, "Width")
plotViol(plotDfNonZeros, "Mean")
plotViol(plotDfNonZeros, "Var")
```

#### Transcripts with 95% CI of one is less than 5% CI of other (GS Dominates)
```{r}
GSLargeInds <- which(txiInfRepBoot$conf[[2]][nZeroInds,2] < txiInfRepGS$conf[[2]][nZeroInds,1])
bootLargeInds <- which(txiInfRepGS$conf[[2]][nZeroInds,2] < txiInfRepBoot$conf[[2]][nZeroInds,1])

print(length(GSLargeInds))
print(length(bootLargeInds))

pGSLargeDf <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[2]], "GS" = txiInfRepGS$conf[[2]]), 
                               list("Boot" = nZeroInds[GSLargeInds], "GS" = nZeroInds[GSLargeInds]))
plotHist(pGSLargeDf, "Width")
plotHist(pGSLargeDf, "Mean")
plotHist(pGSLargeDf, "HighC")
plotHist(pGSLargeDf, "LowC")
```

#### Transcripts with 95% CI of one is less than 5% CI of other (Bootstrap Dominates)
```{r}
pBootLargeDf <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[2]], "GS" = txiInfRepGS$conf[[2]]), 
                               list("Boot" = nZeroInds[bootLargeInds], "GS" = nZeroInds[bootLargeInds]))
plotViol(pBootLargeDf, "Width")
plotViol(pBootLargeDf, "Mean")
plotViol(pBootLargeDf, "HighC")
plotViol(pBootLargeDf, "LowC")
```

#### Computing the difference between magnitude of difference b/w the two
```{r}
diffs <- txiInfRepGS$conf[[2]][nZeroInds,"Width"] - txiInfRepBoot$conf[[2]][nZeroInds,"Width"]
print(sum(diffs < 0))
print(sum(diffs > 0))
hist(diffs)

print(sum(abs(diffs) < 20))
print(sum(diffs < -20))
print(sum(diffs > 20))
```

Of the total 46K transcripts that have non zero counts, around 35K have a difference of less than 20

### Real Data

#### Obtaining the transcripts with zero counts
```{r}
i=1
zeroBInds <- which(txiInfRepBoot$counts[,i] == 0)
zeroGSInds <- which(txiInfRepGS$counts[,i] == 0)
print(length(zeroGSInds))
print(length(zeroBInds))
print(length(setdiff(zeroGSInds, zeroBInds)))
print(length(setdiff(zeroBInds, zeroGSInds)))
```

#### Obtaining transcripts that have zero means over the bootstrap runs
```{r}
zeroMeanGS <- which(txiInfRepGS$conf[[i]][,3] <= 3)
zeroMeanB <- which(txiInfRepBoot$conf[[i]][,3] <= 3)

print(length(zeroMeanGS))
print(length(zeroMeanB))
print(length(setdiff(zeroBInds, zeroMeanB)))
print(length(setdiff(zeroGSInds, zeroMeanGS)))
print(length(intersect(zeroMeanB, zeroMeanGS)))

plotDfZeros <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[i]], "GS" = txiInfRepGS$conf[[i]]), list("Boot" = setdiff(zeroBInds, zeroMeanB), "GS" = setdiff(zeroGSInds, zeroMeanGS)))
plotHist(plotDfZeros, "Width")
plotHist(plotDfZeros, "Mean")
plotHist(plotDfZeros, "Var")
```

#### Only observing the transcripts having non zero counts
```{r}
nZeroInds <- setdiff(1:nrow(txiInfRepBoot$conf[[i]]), union(zeroBInds, zeroGSInds))
print(length(nZeroInds))
plotDfNonZeros <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[i]], "GS" = txiInfRepGS$conf[[i]]), 
                               list("Boot" = nZeroInds, "GS" = nZeroInds))
plotViol(plotDfNonZeros, "Width")
plotViol(plotDfNonZeros, "Mean")
plotViol(plotDfNonZeros, "Var")
```

#### Transcripts with 95% CI of one is less than 5% CI of other (GS Dominates)
```{r}
GSLargeInds <- which(txiInfRepBoot$conf[[i]][nZeroInds,2] < txiInfRepGS$conf[[i]][nZeroInds,1])
bootLargeInds <- which(txiInfRepGS$conf[[i]][nZeroInds,2] < txiInfRepBoot$conf[[i]][nZeroInds,1])

print(length(GSLargeInds))
print(length(bootLargeInds))

pGSLargeDf <- createPlotDf(list("Boot" = txiInfRepBoot$conf[[i]], "GS" = txiInfRepGS$conf[[i]]), 
                               list("Boot" = nZeroInds[GSLargeInds], "GS" = nZeroInds[GSLargeInds]))
plotHist(pGSLargeDf, "Width")
plotHist(pGSLargeDf, "Mean")
plotHist(pGSLargeDf, "HighC")
plotHist(pGSLargeDf, "LowC")
```

#### Computing the difference between magnitude of difference b/w the two
```{r}
diffs <- txiInfRepGS$conf[[i]][nZeroInds,"Width"] - txiInfRepBoot$conf[[i]][nZeroInds,"Width"]
print(sum(diffs < 0))
print(sum(diffs > 0))
hist(diffs)

print(sum(abs(diffs) < 20))
print(sum(diffs < -20))
print(sum(diffs > 20))
```